Timeliness of security updates for Android

### 2014-08-06 securityupdates.tex
Add draft of contributions of paper

>>>>

The contributions of this paper are:
\begin{itemize}
 \item We quantify the vulnerability of Android to root equivalent vulnerabilities.
 \item We characterise the Android update ecosystem.
 \item We measure the security of Android according to three metrics and compare different manufacturers. and device models to allow consumers to differentiate between them based on security.
 \item We investigate the time-lines of vulnerabilities in Android.
 \item We provide models of how the distribution of Android versions changes allowing future version distributions to be predicted.
 \item We propose methods which could be used to improve the situation in future.
\end{itemize}
